\documentclass[9pt,a4paper]{article}
\usepackage[margin=1cm,landscape]{geometry}
\usepackage[T1]{fontenc}
\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  headheight=1cm,
  top=1cm,
  bottom=1.5cm,
  footskip=1cm,
  %showframe
}

%\usepackage{lipsum}

\usepackage{hyperref} % For hyperlinks
\hypersetup{
    colorlinks=true,
    %linkcolor=blue,
    %filecolor=magenta,
    urlcolor=cyan,
}

\usepackage{multicol} % For overall column layout
\usepackage{xcolor} % For colors
\usepackage{tabularx}
\usepackage{fancyhdr} % For footer

\pagenumbering{gobble} % No page numbering
\pagestyle{fancy}
\fancyhead{} % No header
\renewcommand{\headrulewidth}{0pt} % No header rule

\cfoot{\copyright~2019 Canonical} % Actual footer text

% A bunch of command for boilerplate text
\newcommand{\clicmd}[1]{\textbf{\sffamily\color{blue}#1}~~}
\newcommand{\cliverb}[1]{{\sffamily\color{blue}#1}~~}
\newcommand{\cliopt}[1]{{\sffamily#1}~~}
\newcommand{\textangles}[1]{\textless #1\textgreater}
\newcommand{\smallhspace}{\-\hspace{0.3cm}}
\newcommand{\terminal}[1]{\-\hspace{0.5cm}{\sffamily\$ #1}}
\newcommand{\terminalinebreak}[1]{\ \textbackslash\hfill\phantom{.}\linebreak\-\hspace{0.5cm}~}
\newcommand{\ddash}{-{}-}
\newcommand{\deprecated}[1]{{\color{orange}(deprecated)#1}}

\begin{document}
\setlength\parindent{0pt}
\begin{multicols*}{3}[]

\begin{center}
  \textbf{\Large ROS 2 Cheat Sheet}
\end{center}
%

\hrulefill

\textbf{Command Line Interface}

%
All ROS 2 CLI tools start with the prefix `ros2' followed by a command,
a verb and (possibly) positional/optional arguments.

For any tool, the documentation is accessible with,\\
%
\terminal{ros2 \clicmd{command} \ddash help}\\
%
and similarly for verb documentation,\\
%
\terminal{ros2 \clicmd{command} \cliverb{verb} -h}

Similarly, auto-completion is available for all commands/verbs and
most positional/optional arguments. E.g.,\\
%
\terminal{ros2 \clicmd{command} [tab][tab]}

Some of the examples below rely on:\\
\href{https://github.com/ros2/demos}{ROS 2 demos package}.

\hrulefill

%
\clicmd{action} Allows to manually send a goal and
displays debugging information about actions.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{info}        & Output information about an action. \\
\smallhspace \cliverb{list}        & Output a list of action names.      \\
\smallhspace \cliverb{send\_goal}  & Send an action goal.                \\
\smallhspace \cliverb{show}        &  Output the action definition.
\end{tabularx}
%
Examples:
\\
\terminal{ros2 action info /fibonacci} \\
\terminal{ros2 action list} \\
\terminal{ros2 action send\_goal /fibonacci
\terminalinebreak~action\_tutorials/action/Fibonacci "{order: 5}"} \\
\terminal{ros2 action show action\_tutorials/action/Fibonacci}

\vspace*{.2in}
\hrulefill

%
\clicmd{bag} Allows to record/play topics to/from a rosbag.
\\
Verbs:
\\
%
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{info}      & Output information of a bag.\\
\smallhspace \cliverb{play}      & Play a bag.\\
\smallhspace \cliverb{record}    & Record a bag.
\end{tabularx}
%
\\
Examples:
\\
\terminal{ros2 info \textangles{bag-name}}\\
\terminal{ros2 play \textangles{bag-name}}\\
\terminal{ros2 record -a}
%

\vfill\null
\columnbreak

\hrulefill

%
\clicmd{launch} Allows to run a launch file in an arbitrary package
without to `cd' there first.
\\
Usage:
\\
\terminal{ros2 launch \textangles{package}~\textangles{launch-file}}
\\
Example:
\\
\terminal{ros2 launch demo\_nodes\_cpp add\_two\_ints.launch.py}
%

\vspace*{.2in}
\hrulefill

%
\clicmd{msg} Displays debugging information about messages.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{list}      & Output a list of message types.                           \\
\smallhspace \cliverb{package}   & Output a list of message types within a given package.    \\
\smallhspace \cliverb{packages}  & Output a list of packages which contain messages.         \\
\smallhspace \cliverb{show}      & Output the message definition.
\end{tabularx}
%
Examples:
\\
\terminal{ros2 msg list} \\
\terminal{ros2 msg package std\_msgs} \\
\terminal{ros2 msg packages} \\
\terminal{ros2 msg show geometry\_msgs/msg/Pose}
%


\vspace*{.2in}
\hrulefill

%
\clicmd{node} Displays debugging information about nodes.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{info}   & Output information about a node. \\
\smallhspace \cliverb{list}   & Output a list of available nodes.
\end{tabularx}
%
Examples:
\\
\terminal{ros2 node info /talker} \\
\terminal{ros2 node list}
%

\vfill\null
\columnbreak

\hrulefill

%
\clicmd{param} Allows to manipulate parameters.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{delete}    & Delete parameter.                         \\
\smallhspace \cliverb{get}       & Get parameter.                            \\
\smallhspace \cliverb{list}      & Output a list of available parameters.    \\
\smallhspace \cliverb{set}       & Set parameter
\end{tabularx}
%
Examples:
\\
\terminal{ros2 param delete /talker /use\_sim\_time}    \\
\terminal{ros2 param get /talker /use\_sim\_time}       \\
\terminal{ros2 param list}                              \\
\terminal{ros2 param set /talker /use\_sim\_time false}
%

\vspace*{.2in}
\hrulefill

%
\clicmd{pkg} Create a ros2 package or output package(s)-related information.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{create}        &  Create a new ROS2 package.                       \\
\smallhspace \cliverb{executables}   &  Output a list of package specific executables.   \\
\smallhspace \cliverb{list}          &  Output a list of available packages.             \\
\smallhspace \cliverb{prefix}        &  Output the prefix path of a package.             \\
\end{tabularx}
%
Examples:
\\
\terminal{ros2 pkg executables demo\_nodes\_cpp}    \\
\terminal{ros2 pkg list}                            \\
\terminal{ros2 pkg prefix std\_msgs}                \\
%


\hrulefill

%
\clicmd{run} Allows to run an executable in an arbitrary package
without having to `cd' there first.
\\
Usage:
\\
\terminal{ros2 run \textangles{package}~\textangles{executable}}
\\
Example:
\\
\terminal{ros2 run demo\_nodes\_cpp talker}
%

\vfill\null
\columnbreak

\hrulefill

%
\clicmd{service} Allows to manually call a service and displays debugging
information about services.
\\
Verbs:
\\
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{call}   & Call a service.                            \\
\smallhspace \cliverb{list}   & Output a list of service names.            \\
\end{tabularx}
%
Examples:
\\
\terminal{ros2 service call /add\_two\_ints
\terminalinebreak~example\_interfaces/AddTwoInts "\{a: 1, b: 2}\}"  \\
\terminal{ros2 service list}                                      \\
%

\vspace*{.2in}
\hrulefill

%
\clicmd{srv} Various srv related verbs.
\\
Verbs:
\\
%
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{list}      & Output a list of available service types.\\
\smallhspace \cliverb{package}   & Output a list of available service types within one package.\\
\smallhspace \cliverb{packages}  & Output a list of packages which contain services.\\
\smallhspace \cliverb{show}      & Output the service definition.
\end{tabularx}
%


\vfill\null
\columnbreak
\hrulefill

%
\clicmd{topic} A tool for displaying debug information about ROS topics,
including publishers, subscribers, publishing rate, and
messages.
\\
Verbs:
\\
%
\begin{tabularx}{\linewidth}{lX}
\smallhspace \cliverb{bw}    & Display bandwidth used by topic.                  \\
\smallhspace \cliverb{delay} & Display delay of topic from timestamp in header.  \\
\smallhspace \cliverb{echo}  & Output messages of a given topic to screen.       \\
\smallhspace \cliverb{hz}    & Display publishing rate of topic.                 \\
\smallhspace \cliverb{info}  & Output information about a given topic.           \\
\smallhspace \cliverb{list}  & Output list of active topics.                     \\
\smallhspace \cliverb{pub}   & Publish data to a topic.                          \\
\end{tabularx}
%
Examples:
\\
\terminal{ros2 topic bw /chatter}                         \\
\terminal{ros2 topic echo /chatter}                       \\
\terminal{ros2 topic hz /chatter}                         \\
\terminal{ros2 topic info /chatter}                       \\
\terminal{ros2 topic list}                                \\
\terminal{ros2 topic pub /chatter std\_msgs/msg/String
\terminalinebreak~'data: Hello ROS 2 world'}              \\
\terminal{ros2 topic type /rosout}                        \\

\end{multicols*}
\end{document}
